\bf Climbing

### 2021-07-26 manuscript/Rmd/draft.Rmd
Create Rmd manuscript folder

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      message = FALSE, 
                      warning = FALSE,
                      comment = "",
                      fig.width = 5,
                      fig.height = 4,
                      results = "asis")
options(xtable.comment = FALSE,
        xtable.caption.placement = "top", 
        xtable.include.rownames = FALSE)
```

@@

Copy from Rnw + Edit

@@

@@

We collected data on major climbing competitions from 2018 to 2020, including the 2020 Continental Championships of Europe, Africa, Oceania, Pan-America; 2019 and 2018 World Championships; 2018 Asian Games; and 2018 Asian Games. We are interested in looking at the relationships between the ranks of the individual events and the final standings, and we computed Kendall’s Tau (Kendall Rank Correlation Coefficient).

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      message = FALSE, 
                      warning = FALSE,
                      comment = "",
                      # fig.width = 5,
                      # fig.height = 4,
                      results = "asis")
options(xtable.comment = FALSE,
        xtable.caption.placement = "top", 
        xtable.include.rownames = FALSE)
```

@@

(Copy from Rnw + Edit)

## Sport Climbing

## Other Scoring Methods

@@

We collected data on major climbing competitions from 2018 to 2020, including the 2020 Continental Championships of Europe, Africa, Oceania, Pan-America; 2019 and 2018 World Championships; 2018 Asian Games; and 2018 Asian Games.

@@

Using past competitions data, w are interested in looking at the relationships between the ranks of the individual events and the final standings, and we computed Kendall’s Tau (Kendall Rank Correlation Coefficient).

@@

A single climber excluded changes things drastically, espcially order of medalists.

The cases where someone behind you drops out and your ranking changes.

```{r}
women_final <- read_csv("https://raw.githubusercontent.com/qntkhvn/climbing/main/data/2018_youth_olympics/women_final.csv")
rerank <- list()
for (i in 1:nrow(women_final)){
  rerank[[i]] <- women_final[-i,] %>%
    mutate(rank_drop = i)
}

rerank_df <- women_final %>% 
  mutate(rank_drop = 0) %>% 
  bind_rows(rerank) %>% 
  group_by(rank_drop) %>% 
  mutate(speed = rank(speed),
         bould = rank(bould),
         lead = rank(lead),
         total = speed * bould * lead) %>% 
  arrange(total, .by_group = TRUE) %>% 
  ungroup() %>% 
  group_by(rank_drop, total) %>% 
  mutate(speed_tb = ifelse(speed < lag(speed), 1, 0),
         bould_tb = ifelse(bould < lag(bould), 1, 0),
         lead_tb = ifelse(lead < lag(lead), 1, 0),
         tb = speed_tb + bould_tb + lead_tb,
         tb = ifelse(is.na(tb), 1, tb)) %>% 
  ungroup() %>% 
  group_by(rank_drop) %>% 
  arrange(total, -tb, .by_group = TRUE) %>% 
  mutate(rank = row_number())
```

```{r, fig.cap = "Original rankings and rankings after each rank is dropped"}
rerank_df %>% 
  mutate(last = fct_reorder(last, -rank)) %>% 
  # filter(rank_drop %in% c(0, 5)) %>% 
  ggplot(aes(x = last, y = total)) +
  geom_col() +
  geom_text(aes(label = rank), hjust = -0.1, size = 3) +
  coord_flip() +
  facet_wrap(~ rank_drop) +
  labs(y = "Score",
       x = "Climber")
```

### 2021-07-26 manuscript/Rmd/draft.tex
Create Rmd manuscript folder

Copy from Rnw + Edit

@@

We collected data on major climbing competitions from 2018 to 2020,
including the 2020 Continental Championships of Europe, Africa, Oceania,
Pan-America; 2019 and 2018 World Championships; 2018 Asian Games; and
2018 Asian Games. We are interested in looking at the relationships
between the ranks of the individual events and the final standings, and
we computed Kendall's Tau (Kendall Rank Correlation Coefficient).

@@

>>>>

(Copy from Rnw + Edit)

\hypertarget{sport-climbing}{%
\subsection{Sport Climbing}\label{sport-climbing}}

\hypertarget{other-scoring-methods}{%
\subsection{Other Scoring Methods}\label{other-scoring-methods}}

@@

Using past competitions data, w are interested in looking at the
relationships between the ranks of the individual events and the final
standings, and we computed Kendall's Tau (Kendall Rank Correlation
Coefficient).

@@

A single climber excluded changes things drastically, espcially order of
medalists.

The cases where someone behind you drops out and your ranking changes.

\begin{figure}
\centering
\includegraphics{draft_files/figure-latex/unnamed-chunk-12-1.pdf}
\caption{Original rankings and rankings after each rank is dropped}
\end{figure}
